Monte Carlo tree search compared to A\(^*\) in airspace configuration decision problem

### 2018-05-21 article/article.tex
(~) Small corrections

The graph~\ref{fig:cmpdepth} shows the evolution of the difference of costs with
varying depth. The error rate is expected to grow as the depth increase since
the MCTS might fail to explore the best nodes among the exponentially growing
amount of them.
\begin{figure}
  \begin{tikzpicture}
    \begin{axis}
      [line width=0.05, mark size=0.1, xlabel=depth, ylabel=cost,
      legend entries = {A\(^*\), MCTS}]
      \foreach \i in {0, 1} {%
        \addplot+ table [
          x expr = {\lineno + 1}, y index = \i ] {./data/cmpdepth.data};
      }
    \end{axis}
  \end{tikzpicture}
  \caption{Cost difference for varying depth with 0.5 seconds allowed to
    MCTS.}\label{fig:cmpdepth}
\end{figure}

@@

The resulting graphs are shown in figure~\ref{fig:longterm} in which it can be
seen that the algorithm reaches its best cost when it runs for 2 seconds per
step.

The converging speed may also depend on the depth of the tree searched through.
The figure~\ref{fig:timedepth} shows
\begin{figure}
  \begin{tikzpicture}
    \begin{axis}
      [line width=0.05, mark size=0.1, xlabel=time(s), ylabel=cost]
      \addplot+ table {data/shortterm.data};
    \end{axis}
  \end{tikzpicture}
  \caption{Monte Carlo tree search called with varying time allowed to compute
  each step, with a depth of 40 and \(\theta = 11\). The cost seems to be
  approximately stable from \(t=0.5\)s.}\label{fig:shortterm}
\end{figure}

@@

\paragraph{Further work}
Since all the tests has been run using the same fictitious area with the same
trafic, neither the influence of the complexity of the airspace nor of the
trafic have been assessed. It would be thus relevant to carry further tests on
bigger areas with differing trafic. This can be emphasised
by~\cite{ferrari2017}, in which the time needed to compute the cost with A\(^*\)
depends heavily on the trafic itself.

>>>>

The graph~\ref{fig:cmpdepth} shows the evolution of the difference of costs with
varying depth. The error rate is expected to grow as the depth increase since
the MCTS might fail to explore the best nodes among the exponentially growing
amount of them. The figure~\ref{fig:cmpdepth} does not show a constant growth of
error rate between MCTS and A\(^*\). As hoped, the MCTS remains always better
than the greedy algorithm.
\begin{figure}
  \begin{tikzpicture}
    \begin{axis}
      [line width=0.05, mark size=0.1, xlabel=depth, ylabel=cost,
      legend entries = {A\(^*\), MCTS, Greedy}, legend pos=south east]
      \foreach \i in {0, 1, 2} {%
        \addplot+ table [
          x expr = {\lineno + 1}, y index = \i ] {./data/cmpdepth.data};
      }
    \end{axis}
  \end{tikzpicture}
  \caption{Cost difference for varying depth with 0.5 seconds allowed to
    MCTS.}\label{fig:cmpdepth}
\end{figure}

@@

The resulting graphs are shown in figure~\ref{fig:shortterm} in which it can be
seen that the algorithm reaches its best cost when it runs for 1 second per
step, but the cost is approximately stable from 0.5 seconds.
\begin{figure}
  \begin{tikzpicture}
    \begin{axis}
      [line width=0.05, mark size=0.1, xlabel=time(s), ylabel=cost]
      \addplot+ table {data/shortterm.data};
    \end{axis}
  \end{tikzpicture}
  \caption{Monte Carlo tree search called with varying time allowed to compute
  each step, with a depth of 40 and \(\theta = 11\). The cost seems to be
  approximately stable from \(t=0.5\)s.}\label{fig:shortterm}
\end{figure}

@@

\paragraph{Further work}
Since all the tests has been run using the same fictitious area with the same
trafic, neither the influence of the complexity of the airspace nor of the
trafic have been assessed. It would be thus relevant to carry further tests on
bigger areas with heavier and differing trafic. This can be emphasised
by~\cite{ferrari2017}, in which the time needed to compute the cost with A\(^*\)
depends heavily on the trafic itself.
